E Coli Project Paper Incredibly Rough Draft

### 2013-08-27 paper/paper.tex
minor changes to plotting legend, movie scale, and paper adding figures, have not added these figs to makefile yet

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
  \caption{Total protein fluctuation in the right, middle, and
    left parts of a 4$\mu m$ by 1$\mu m$ pill shaped cell.  The
    different forms of protein changes while the total number of
    proteins remains constant.}
  \label{total-oscillation-plot-40-05-0-0-150}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
  \caption{Total protein fluctuation in the right, middle, and
    left parts of a 2$\mu m$ by 1$\mu m$ pill shaped cell.}
  \label{total-oscillation-plot-20-05-0-0-150}
\end{figure}

Make sure to talk about length of periods as well

Figure \ref{total-oscillation-plot-40-05-0-0-150} shows results for a
pill shaped cell of length $4\mu$ and radius $.5\mu$.  The plot shows
both the transerence between different protein compounds and movement
within the cell.  Starting at the beginning of a period, we can see
that first there is a spike
